\documentclass[10pt,letterpaper,draft]{report}
\usepackage[utf8]{inputenc} \usepackage{amsmath} \usepackage{amsfonts}
\usepackage{hyperref}
\usepackage{ctable}
\usepackage{graphicx}
\usepackage{amssymb} \usepackage{ifdraft} \ifdraft {
  \usepackage[paperwidth=275.9mm, paperheight=279.4mm]{geometry}
  \setlength{\evensidemargin}{95mm}
  \usepackage[colorinlistoftodos,obeyDraft]{todonotes} } {
  \usepackage[left=1in,right=1in,top=1in,bottom=1in,paperwidth=275.9mm,
  paperheight=279.4mm]{geometry} \usepackage[obeyDraft]{todonotes} }

\usepackage[section]{placeins}
% \usepackage{minted}

\usepackage{longtable}

\author{Devin Schwab\\
  Mark Schultz\\
  David Jannotta\\
  Eddie Massey III}
\title{EECS 376/476 Mobile Robotics\\
  Team Alpha Midterm Report} \date{May 3, 2012}
\begin{document}
\bibliographystyle{IEEEtran}
\listoftodos
\maketitle

\tableofcontents
\newpage

\input{overview}

\input{software_architecture}

\input{node_details}

\input{demo_code}

\part{Conclusion}

This semester we accomplished a lot of complex tasks with the robot such as following a strap using vision and depth information. We also designed a general purpose framework for movement that was going to be used in the final demo had it been completed in time. In addition we developed algorithms for velocity profiler that in practice worked far better than simple integration. Over the semester our team had many accomplishments such as being the first to figure out the transformation code and being the farthest along in understanding and using the costmap. Almost to the point where it was useable. Had we more time We could have finished the entire stack.

If we were to work more on this after finishing the movement stack we would have spent time developing algorithms to do autonomous planning given a set of goals. Possible approaches to this would have been to model the environment and use a Markov Decision Process (MDP) or even to implement a type of reinforcement learning algorithm, such as Q learning, so that the robot would gain experience over time.

\section{Acknowledgements}
Our team would like to express our appreciation for the class and all that we learned this semester. We would also like to thank the other teams. Everyone was extremely helpful and it was often useful to gain insight into other approaches. We believe that inter-team cooperation was a great benefit in our learning experiences.

\bibliography{bibliography}

\appendix
\chapter{Git Statistics}


\end{document}
%%% Local Variables: 
%%% mode: latex
%%% TeX-master: t
%%% End: 
